Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-01-20 ms.tex
added a time series of the GL dewar test with a background subtraction box.

\begin{figure*}
\gridline{\fig{ap_labels_S02illum_GLrun104.pdf}{0.32\textwidth}{Apertures}
		\fig{raw_tser_phot_S02illum1miAll_GLrun104.pdf}{0.32\textwidth}{Raw time series}
		\fig{refcor_phot_S02illum1miAll_GLrun104.pdf}{0.32\textwidth}{Ratio Time Series}}
\caption{The precision of this short-duration GL dewar test was the extremely high at $\sigma=$240 ppm after stabilization.
}\label{fig:GLtSeries}
\end{figure*}

>>>>

\begin{figure*}
\gridline{\fig{ap_labels_S02illum_GLrun104.pdf}{0.32\textwidth}{Apertures}
		\fig{raw_tser_phot_S02illum1miAll_GLrun104.pdf}{0.32\textwidth}{Raw time series}
		\fig{refcor_phot_S02illum1miAll_GLrun104.pdf}{0.32\textwidth}{Ratio Time Series}}
\caption{The precision of this short-duration GL dewar test was the extremely high at $\sigma=$240 ppm after stabilization, if we remove absolute changes likely due to the lamp.
}\label{fig:GLtSeries}
\end{figure*}

\begin{figure*}
\gridline{\fig{ap_labels_S02illum1miAllBacksub_GLrun104.pdf}{0.32\textwidth}{Apertures}
		\fig{raw_tser_phot_S02illum1miAllBacksub_GLrun104.pdf}{0.32\textwidth}{Raw time series}
		\fig{refcor_phot_S02illum1miAllBacksub_GLrun104.pdf}{0.32\textwidth}{Ratio Time Series}}
\caption{The same time series as Figure \ref{fig:GLtSeries} but with a rectangular aperture subtraction box.
}\label{fig:GLtSeriesBacksub}
\end{figure*}
